Teaching Low-Level Concurrency with \pebbles and \landslide

### 2016-08-23 sigcse-17/landslide.tex
sigcse: talk about heuristix

TODO talk about heuristics

>>>>

Student submissions may behave in extraordinary ways which violate the assumptions of many modern model checkers.
Landslide refuses to test code which fails the hurdle criteria (\sect{\ref{sec:grading}}),
but it must support testing any legal, yet distasteful, solution.
%Hence, we added several heuristic
For example, students may use open-coded \x{yield} or \x{xchg} loops rather than the mutex abstraction. %(though it is discouraged).
To avoid getting stuck in a cyclic (infinite) state space, Landslide keeps a ``yield loop'' counter for each thread;
when a thread \x{yield}s 10 times without otherwise making progress, Landslide marks it blocked.
%
In extreme cases, this may erroneously seem like deadlock when all threads \x{yield} many times coincidentally.
To avoid wasting student time with false alarms, % the ultimate sin
Landslide will reset all blocked threads' yield-loop counters,
retrying potentially up to 128 times before reporting a true deadlock.

Students may also break abstraction by open-coding a \x{mutex_unlock} sequence.
Landslide must track lock operations for accurate data-race analysis,
so to catch these patterns, it
%learns the size of the \x{mutex} struct, then
checks accesses against stored lock addresses blocked on by other threads.
Similarly, these rogue unlock accesses may unblock a yield-looping thread.
